Inference of Bifurcations\\with Differentiable Continuation

### 2021-05-17 docs/article.tex

\begin{figure}
\centering
\includegraphics[width=11cm]{saddle-node}
\caption{Saddle-node model $\rates(z) = p + \theta_{1}u+\theta_{2}u^3$ with $\theta=(5/2,-1)$ and targets $\targets=\{-1,1\}$. Determinant in red. Lighter shades indicate the determinant crossing zero for unstable solutions}
\label{fig:saddle-node}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=11cm]{pitchfork}
\caption{Pitchfork model $\rates(z) = \theta_{1} + p u+\theta_{2}u^3$ with $\theta=(1/2,-1)$ and target $\targets=\{0\}$. Determinant in red. Lighter shades indicate the determinant crossing zero for unstable solutions}
\label{fig:pitchfork}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=6cm]{saddle-node}
\includegraphics[width=6cm]{pitchfork}
\caption{Saddle-node model $\rates(z) = p + \theta_{1}u+\theta_{2}u^3$ and pitchfork model $\rates(z) = \theta_{1} + p u+\theta_{2}u^3$ with $\theta=(5/2,-1),(1/2,-1)$ and targets $\targets=\{-1,1\},\{0\}$ respectively. Determinant in red. Lighter shades indicate the determinant crossing zero for unstable solutions}
\label{fig:minimal-models}
\end{figure}
